Exoplanet population inference and the rate of Earth analogs \\ from noisy, incomplete catalogs

### 2014-06-04 document/ms.tex
adding correct emcee ref

\begin{figure}[p]
\begin{center}
\includegraphics[width=\textwidth]{figures/smooth/results.pdf}
\end{center}
\caption{%
{\bf Simulated data}.
Inferences about the occurrence rate function based on the simulated catalog
\modela.
\emph{Center:} the points with error bars show the exoplanet candidates in the
simulated incomplete catalog, the contours show the survey completeness
function (\citealt{petigura}), and the grayscale shows the median posterior
occurrence surface.
\emph{Top and left:} the red dashed line shows the \emph{true} distribution
that was used to generate the catalog, the points with error bars show the
results of the inverse-detection-efficiency procedure, and the histograms are
posterior samples from the marginalized occurrence rate as inferred by our
method.
\figlabel{smooth-results}}
\end{figure}

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=\textwidth]{figures/results/results.pdf}
\end{center}
\caption{%
The same as \fig{smooth-results} when applied to the observed data from
\citet{petigura}.
\figlabel{real-results}}
\end{figure}

\begin{figure}[p]
\begin{center}
\includegraphics{figures/results/period.pdf}
\end{center}
\caption{%
The period distribution.
\figlabel{period}}
\end{figure}

\begin{figure}[p]
\begin{center}
\includegraphics{figures/results/radius.pdf}
\end{center}
\caption{%
The radius distribution.
\figlabel{radius}}
\end{figure}

\begin{figure}[p]
\begin{center}
\includegraphics{figures/results/linear-radius.pdf}
\end{center}
\caption{%
The radius distribution.
\figlabel{linear-radius}}
\end{figure}

@@

\bibitem[Foreman-Mackey \etal(2012)]{emcee}
\dfmtodo{THE FUCK}

>>>>

\begin{figure}[p]
\begin{center}
\includegraphics[width=\textwidth]{figures/smooth/results.pdf}
\end{center}
\caption{%
{\bf Simulated data}.
Inferences about the occurrence rate function based on the simulated catalog
\modela.
\emph{Center:} the points with error bars show the exoplanet candidates in the
simulated incomplete catalog, the contours show the survey completeness
function (\citealt{petigura}), and the grayscale shows the median posterior
occurrence surface.
\emph{Top and left:} the red dashed line shows the true distribution that was
used to generate the catalog, the points with error bars show the results of
the inverse-detection-efficiency procedure, and the histograms are posterior
samples from the marginalized occurrence rate as inferred by our method.
\figlabel{smooth-results}}
\end{figure}

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=\textwidth]{figures/results/results.pdf}
\end{center}
\caption{%
{\bf Real data}.
The same as \fig{smooth-results} when applied to the observed data from
\citet{petigura}.
\emph{Center:} the points with error bars show the catalog measurements, the
contours show the survey completeness function, and the grayscale shows the
median posterior occurrence surface.
\emph{Top and left:} the points with error bars show the results of the
inverse-detection-efficiency procedure, and the histograms are posterior
samples from the marginalized occurrence rate as inferred by our method.
\figlabel{real-results}}
\end{figure}

\begin{figure}[p]
\begin{center}
\includegraphics{figures/results/period.pdf}
\end{center}
\caption{%
{\bf Real data}.
The occurrence rate as a function of logarithmic period integrated over bins
in logarithmic radius.
The lines with error bars show the posterior sample median and 68th
percentile and the line style specifies the radius bin.
The period distribution for the largest planets in the sample
($8 \le R/R_\oplus < 32$) continues to increase (as a function of
$\ln\period$) for all periods while the distribution seems to flatten and
turn over at periods around 50 days.
\figlabel{period}}
\end{figure}

\begin{figure}[p]
\begin{center}
\includegraphics{figures/results/radius.pdf}
\end{center}
\caption{%
{\bf Real data}.
The occurrence rate as a function of logarithmic radius integrated over bins
in logarithmic period.
The lines with error bars show the posterior sample median and 68th
percentile and the line style specifies the period bin.
The distributions in all the period bins are qualitatively consistent and
there are plausibly features near $R\sim3\,R_\oplus$ and $R\sim10\,R_\oplus$.
\figlabel{radius}}
\end{figure}

\begin{figure}[p]
\begin{center}
\includegraphics{figures/results/linear-radius.pdf}
\end{center}
\caption{%
{\bf Real data}.
The same as \fig{radius} but presented as a density in radius instead of
logarithmic radius.
\figlabel{linear-radius}}
\end{figure}

@@

\bibitem[Foreman-Mackey \etal(2012)]{emcee}
Foreman-Mackey, D., Hogg, D.~W., Lang, D., \& Goodman, J.\ 2013, \pasp, 125,
306 (\arxiv{1202.3665})
